Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-17 reanalysis-3-propensity_scores.qmd
balance table bug

  # Get balance table - use summary or bal.table depending on what works
  balance_table <- tryCatch({
    # Try to get balance table
    if (!is.null(twang_model$balance.es.mean)) {
      twang_model$balance.es.mean
    } else if (!is.null(twang_model$balance)) {
      twang_model$balance
    } else {
      # Extract from summary
      summary(twang_model)$es.mean.ATT
    }
  }, error = function(e) {
    # If all else fails, create a simple balance assessment
    NULL
  })

@@

  # Use bal.table to get balance statistics
  # This function should work with the ps object
  bal_table <- tryCatch({
    bal.table(twang_model, digits = 3)
  }, error = function(e) {
    # If bal.table doesn't work, try summary
    tryCatch({
      summary(twang_model)$es.mean.ATT
    }, error = function(e2) {
      NULL
    })
  })

>>>>

  # Get balance table from summary
  balance_table <- tryCatch({
    sum_obj <- summary(twang_model)
    # Extract the balance table for es.mean
    if (!is.null(sum_obj$es.mean.ATT)) {
      sum_obj$es.mean.ATT
    } else if (!is.null(sum_obj$es.mean)) {
      sum_obj$es.mean
    } else {
      NULL
    }
  }, error = function(e) {
    NULL
  })

@@

  # Get balance table from the summary
  # When using es.mean only, the balance table is in summary()$es.mean.ATT
  bal_table <- tryCatch({
    # Get the summary and extract balance table
    sum_obj <- summary(twang_model)
    # For single stop method, look for es.mean.ATT
    if (!is.null(sum_obj$es.mean.ATT)) {
      sum_obj$es.mean.ATT
    } else if (!is.null(sum_obj$es.mean)) {
      sum_obj$es.mean
    } else if (!is.null(sum_obj[[1]])) {
      # Sometimes it's the first element
      sum_obj[[1]]
    } else {
      NULL
    }
  }, error = function(e) {
    NULL
  })
